True versus apparent shapes of bow shocks

### 2017-11-26 papers/Paper1/sec-conic.tex
Make graph of departure function for conics
And begin description of it in paper

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figs/conic-departure}
  \caption[]{Parabolic departure function for conic sections.}
  \label{fig:conic-departure}
\end{figure}

\subsection{Parabolic departure function}
\label{sec:parab-depart-funct}

The special case of confocal conic sections
(\(\Lambda = \Pi\)) can be written in polar form as
\begin{equation}
  \label{eq:confocal-polar}
  R(\theta) = R_0 \frac {1 + \ecc} {1 + \ecc \cos \theta}
\end{equation}
where \(\ecc = (1 - \Q)^{1/2}\) is the \textit{conic eccentricity}.
For the confocal parabola (\(\ecc = 1\)), the dimensionless reciprocal
radius is therefore \(R_0/R(\theta) = \tfrac12 (1 + \cos \theta)\), which
suggests the following form for a \textit{departure function} that
measures the difference between a given shape \(R(\theta)\) and the
parabola:
\begin{equation}
  \label{eq:departure-function}
  \Depart\bigl(\cos \theta\bigr) = \frac{R_0} {R(\theta)} - \tfrac12 \left( 1 + \cos \theta \right). 
\end{equation}
From equations~\eqref{eq:confocal-polar} and
\eqref{eq:departure-function} it is clear that \(\Depart\) is a linear
function of \(\cos \theta\) for other confocal conics, being positive for
ellipses (\(\ecc < 1\)) and negative for hyperbolae (\(\ecc > 1\)).
